*flippant* --- An R package for the automated analysis of dithionite scramblase

### 2016-05-21 inst/manuscript/manuscript.rmd
Minor reormatting;
en-dash to em-dash;

---
title: '*flippant* -- An R package for the automated analysis of dithionite scramblase
  assays'
author: Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
  Michael A. Goren ^‡^ and Anant K. Menon ^‡^
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
  html_document:
    fig_caption: yes
csl: bioinformatics.csl
bibliography: flippant.bib
---

>>>>

---
title: '*flippant* --- An R package for the automated analysis of dithionite scramblase
  assays'
author: Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
  Michael A. Goren ^‡^ and Anant K. Menon ^‡^
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
  html_document:
    fig_caption: yes
csl: bioinformatics.csl
bibliography: flippant.bib
---
